Novel crystallization pathway\\and formation of ``colloidal rain'' during viscoelastic phase separation

### 2015-09-23 crystal-gel/crystal_gel_letter.tex
fig:crystal Reconstruction from confocal coordinates. Gray vertical lines

\begin{figure*}
 \centering
 \includegraphics[width=16cm]{oldfig/fig4a}
 \includegraphics[width=8cm]{oldfig/fig4b}
 \includegraphics[width=8cm]{oldfig/fig4c}
 % snapshots.eps: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=0 -1 2256 735
 \caption{
{\bf Crystal gel formation.} 
\textbf{a,} Snapshots of configurations at $\phi=0.25$ and $c_p=0.38$, for t=4856 (left), 12956 (center), 27956 (right). Particles are colored according to their phase. Green: HCP; Red: FCC; blue: BCC; white: liquid or gas. 
 \textbf{b,} Fraction of particles for each phase (between bcc, hcp, fcc, surface, liquid or gas) at $\phi=0.25$ and $c_p=0.38$.
 Crystalline phases are detected through bond orientational analysis~\cite{russo2012microscopic}; surface particles are particles
 with at least two crystalline neighbours; liquid particles have at least 4 neighbours; gas particles are particles with less than 4
 nearest neighbours.
\textbf{c,} Transition probabilities for the same process as in \textbf{b}. Crystal includes all crystalline phases (bcc, hcp, fcc) and surface particles.}
 \label{fig:transitions}
\end{figure*}

In the next section we demonstrate that the volume growth is due to direct condensation of the gas phase on the crystalline seeds.
First we show in Fig.~\ref{fig:transitions}a slabs of 10 particle diameter thickness for configurations at $\phi=0.25$ and $c_p=0.38$ at different times.
Particles are coloured according to their phase. Green: HCP; Red: FCC; blue: BCC; white: liquid or gas. The figure shows the first nucleation
events inside the liquid network (left panel); then these crystalline nuclei grow directly from the gas phase (middle panel), and finally
the different nuclei coalesce (right panel).

>>>>

\begin{figure*}
 \centering
 \includegraphics{fig/crystal.pdf}
 \caption{
{\bf Crystal gel formation.} 
\textbf{a,} Reconstructions from confocal coordinates at $\phi=0.25$ and $c_p=0.38$. Depth of view is $5\sigma$. Particles are drawn to scale and coloured according to their phase. Dark red: crystal; orange: surface of crystal; yellow: liquid; blue: gas. 
 \textbf{b,} Fraction of particles for each phase. Gray vertical lines indicate the times shown in \textbf{a.}
\textbf{c,} Transition probabilities for the same process as in \textbf{b}. Here crystal includes surface particles.}
 \label{fig:transitions}
\end{figure*}

In the next section we demonstrate that the volume growth is due to direct condensation of the gas phase on the crystalline seeds.
First we show in Fig.~\ref{fig:transitions}a slabs of 10 particle diameter thickness for configurations at $\phi=0.25$ and $c_p=0.38$ at different times.
Particles are coloured according to their phase. The figure shows the first nucleation
events inside the liquid network (left panel); then these crystalline nuclei grow directly from the gas phase (middle panel), and finally
the different nuclei coalesce (right panel).
